What\,Agreement\,Hath\,Mars\,With\,Earth? \\ An Exploration of Urbit's IPC Interfaces

### 2024-03-11 mss.tex
Reword abstract.

%  Make first page footer:
\fancypagestyle{firststyle}{%
\fancyhf{}% Clear header/footer
\fancyhead{}
\fancyfoot[L]{{\footnotesize
              %% We toggle between these:
              % Manuscript submitted for review.\\
              {\it Urbit Systems Technical Journal} I:1 (2024):  1–3. \\
              ~ \\
              Address author correspondence to \authorpatp.
              }}
}
%  Arrange subsequent pages:
\fancyhf{}
\fancyhead[LE]{{\urbitfont Urbit Systems Technical Journal}}
\fancyhead[RO]{Urbit's IPC Interfaces}
\fancyfoot[LE,RO]{\thepage}

@@

\begin{abstract}
\noindent \sloppy
The idealistic Maxwellian principles of Urbit are somewhat at odds with the evolved nature of legacy software ecosystems.  In order to facilitate practical computing, Urbit presents several interfaces for communication with external (“Earth”) systems.  Through a comprehensive examination of Urbit's Arvo kernel and Vere runtime, alongside its high-level and low-level {\sc ipc} interfaces (\texttt{\%khan} and \texttt{\%lick}, respectively), we elucidate the architectural mechanisms that facilitate communication and control between these disparate computing realms.  This exposition aims to demystify Urbit's architecture and underscore its potential to bridge the gap between the familiar digital environments of Earth and the untapped possibilities of Martian computing.
\end{abstract}

>>>>

%  Make first page footer:
\fancypagestyle{firststyle}{%
\fancyhf{}% Clear header/footer
\fancyhead{}
\fancyfoot[L]{{\footnotesize
              %% We toggle between these:
              % Manuscript submitted for review.\\
              {\it Urbit Systems Technical Journal} I:1 (2024):  1–3. \\
              ~ \\
              Address author correspondence to \authorpatp.
              }}
}
%  Arrange subsequent pages:
\fancyhf{}
\fancyhead[LE]{{\urbitfont Urbit Systems Technical Journal}}
\fancyhead[RO]{Urbit's {\sc ipc} Interfaces}
\fancyfoot[LE,RO]{\thepage}

@@

\begin{abstract}
\noindent \sloppy
The idealistic Maxwellian principles of a system built on Nock are somewhat at odds with the evolved and tangled nature of legacy software ecosystems.  In order to facilitate practical computing, Urbit presents several interfaces for communication with external (“Earth”) systems.  Through a comprehensive examination of Urbit's Arvo kernel and Vere runtime, alongside its high-level and low-level {\sc ipc} interfaces (\texttt{\%khan} and \texttt{\%lick}, respectively), we elucidate the architectural mechanisms that facilitate communication and control between these disparate computing realms.  This exposition aims to demystify Urbit's architecture and underscore its potential to bridge the gap between the familiar digital environments of Earth and the untapped possibilities of Martian computing.
\end{abstract}
